\chapter{Process}\label{ch:process}

Along the path of this project, we adhered to the Scrum workflow and decided upon splitting
the team into a client-side and server-side team. We split up into two teams so that we
can work efficiently, and focus on implementing either side of Picle to be able to have
a clear and better understanding one specific side.

\section{Scrum}
Scrum workflow is an agile way of managing a project. It entails having a Scrum Board
which contains all the tasks and goals we need to accomplish that are stored in our backlog.
The Scrum Board is maintained on GitLabs issue board on a consistent basis along with
moving our tasks into their appropriate board whether it is in progress, being tested or
completed.

\subsection{Meetings}
During our weekly meetings, we discussed issues and tasks we needed to tackle and achieve
to further develop Picle. The designated chair of the meeting and the person taking down
minutes was changed per meeting so that everyone got the experience of both roles.

During that meeting, we assigned tasks to each member so that their roles are clear throughout
the upcoming sprint. That was necessary so that we could all concurrently work on different
aspects of Picle in order to be more time and work efficient. Adhering to a modular
Model-View-Controller design pattern enabled us to work concurrently.

In addition, we discussed any decisions we need to conclude upon like which API to use or
which DBMS to use. After having all tasks and decisions made clear, we started coding
throughout the specified duration of each sprint. Throughout a sprint, we made sure to
update our Scrum Board, as we worked on tasks, and that we offered help to members of the team.
Moreover, we made sure that we finished all our work during the specified sprint in order
to not fall behind and be capable of meeting the deadlines for our demos.

After each sprint, we took some time in the meeting to review our progress during that
sprint, what challenges we might have encountered and how we overcame them, as well as
present the demo to our TA. We also push to GitLab screenshots of our test coverage,
Checkstyle report, Scrum Board, release with a tag, sprint plan, and sprint review.
